
---
title: How is Mercury Correlated with Dissolved Organic Carbon in Streams?
author:
  - name: Faraz Khan
    email: farazkhan@uregina.ca
    affiliation: University of Regina
    correspondingauthor: true
    footnote: 1
  - name: Britt Hall
    email: britt.hall@uregina.ca
    affiliation: University of Regina
    footnote: 1
 
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
 Levels of dissolved organic carbon and mercury in streams.
keywords: 
  - methylmercury
  - dissolved organic carbon
journal: "Biogeochemistry"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
header-includes:
 \usepackage{float}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r setup, include=FALSE}
# I'm using R-4.0.5, so using date of 2021-05-17
library("dplyr")
library("tidyverse")
library("ggplot2")

```

# Introduction

Dissolved organic carbon (DOC) is highly associated with methylmercury production in freshwater ecosystems. The use of optical instruments such as spectrometers in the study of DOC have led to a greater understanding of the chemical characteristics and origin of DOC. State of the art emission excitation matrices analysis have resulted in a greater understanding of DOC and its associations with MeHg in various freshwater systems such as streams. [@Graham2013].

# Methods

To test these hypotheses, I will sample urban artificial wetlands and wet ponds from sites across Regina and Saskatoon, using methods derived from Strickman and Mitchell (2017). I will then use sediment samples from these sites in mercury methylation assays involving isotope dilution-gas chromatography-inductively coupled plasma mass spectrometry. Samples will be enriched with a stable Hg isotope to determine the Hg methylation rate constants, ambient Hg, and MeHg concentrations. 

# Results

Figure \ref{fig1} is generated using an R chunk.


```{r}
setwd("~/ldpminiproject/Data")

mercurydata <- read_csv("mercurydata.csv")
mercurydata

ggplot(data = mercurydata, 
       mapping = aes(x = mean_doc , y = mean_streamwater_mehg)) +
  geom_point()

setwd("~/ldpminiproject")
```



# Discussion

The results may be able to influence landscape planning and facilitate further insight into the relationship between methylmercury and bioavailability of inorganic mercury in urban environments. A great understanding of the interactions in our built environment and how it contributes to human caused ubiquitous ecological disruption (Policy Horizons 2018) can ensure that we, as a society, move towards more sustainable models of development. Benthic invertebrates are commonly used as indicators of stream water quality [@Lescord2018]. *Baetis* sp. (Ephemeroptera) are used as stream quality indicators for catchments [@Waiser2006].

# References {.unnumbered}
